Mixed language processing increases cross-language phonetic transfer in Bengali-English Bilinguals

### 2021-05-24 draft_glossa-psych/glossa-psych_AM-ID_manuscript.tex
author info and affil

% \pdf* commands provide metadata for the PDF output. ASCII characters only!
\pdfauthor{Full author name}
\pdftitle{Full title}
\pdfkeywords{Full keyword list, separated, by, commas}

@@

\author[]% short form of the author names for the running header. If no short author is given, no authors print in the headers.
{%as many authors as you like, each separated by \AND.
  \spauthor{.\\ 
  \institute{.\\
  \small{.\\
	}
  }
  \AND
  \spauthor{.\\
  \institute{.\\
  \small{.\\
  }
  }%
}

%%%Notes
% bengali sentence--gloss

\begin{document}

@@

Studies which compare bilinguals speakers' phonological systems with monolinguals see them as relatively stable over time. The difference from monolingual norms is interpreted as the cumulative result of cross-language influence over long periods, \cite<e.g.>{guion2003vowel, caramazza1973acquisition}. However, longitudinal studies %(citations) 
and between-subject comparisons of bilingual speakers who differ in the duration of L2 exposure suggest that interaction between the sound systems is dynamic. Over time, increasing exposure to an L2 can reduce effects of L1 influence, leading to a more fine-grained separation and native-like production of foreign contrasts-- e.g. \cite{bohn1992production} 
found that an approximately 7 years' difference in L2 exposure between groups having the same age of acquisition led to a significant difference in the amount of cross-language transfer. These have been interpreted as changes to long-term phonological representations.

@@

These results highlight that beyond interaction during the cognitive processing of sounds, phonetic transfer is ultimately a linguistic phenomenon, and thus subject to language-specific phonological constraints. Therefore, to make meaningful generalizations, it is imperative to consider data from a variety of language pairs. Existing research on phonetic transfer largely revolves around a small set of phonologically related languages. Thus, the present study extends the scope of this research to a new set of languages-- Indian English and Bengali (an Indo-Aryan language).

Since Bengali has a four-way laryngeal contrast, VOT does not encode a binary voiced/voiceless distinction, and moreover is not the only cue for the corresponding phonological categories \citep{dmitrieva2020acoustic}. Thus, the effects of Bengali on English VOT are likely to be affected by additional phonological factors. Thus, avoiding any potential confounds was another reason we chose to focus on vowels as a target for transfer.

>>>>

% \pdf* commands provide metadata for the PDF output. ASCII characters only!
\pdfauthor{Auromita Mitra, Indranil Dutta}
\pdftitle{Mixed language processing increases cross-language phonetic transfer in Bengali-English Bilinguals}
\pdfkeywords{phonetic transfer, vowel formants, Bengali, English}

@@

\author[Auromita \& Indranil]% short form of the author names for the running header. If no short author is given, no authors print in the headers.
{%as many authors as you like, each separated by \AND.
  \spauthor{Auromita Mitra\\ 
  \institute{The EFL University}\\
  \small{%105, Bd. Raspail, 75005 Paris\\
  auromita.mitra@gmail.com}
  }
  \AND
  \spauthor{Indranil Dutta \\
  \institute{Jadavpur University}\\
  \small{%Warmoesberg 26, 1000 Brussel\\
  indranildutta.lnl@jadavpuruniversity.in}
  }%
}
\begin{document}

@@

Studies which compare bilinguals speakers' phonological systems with monolinguals see them as relatively stable over time. The difference from monolingual norms is interpreted as the cumulative result of cross-language influence over long periods, \cite{guion2003vowel, caramazza1973acquisition}. However, longitudinal studies %(citations) 
and between-subject comparisons of bilingual speakers who differ in the duration of L2 exposure suggest that interaction between the sound systems is dynamic. Over time, increasing exposure to an L2 can reduce effects of L1 influence, leading to a more fine-grained separation and native-like production of foreign contrasts-- e.g. \cite{bohn1992production} 
found that an approximately 7 years' difference in L2 exposure between groups having the same age of acquisition led to a significant difference in the amount of cross-language transfer. These have been interpreted as changes to long-term phonological representations.

@@

These results highlight that beyond interaction during the cognitive processing of sounds, phonetic transfer is ultimately a linguistic phenomenon, and thus subject to language-specific phonological constraints. Therefore, to make meaningful generalizations, it is imperative to consider data from a variety of language pairs. Existing research on phonetic transfer largely revolves around a small set of phonologically related languages. Thus, the present study extends the scope of this research to a new set of languages---Indian English and Bengali (an Indo-Aryan language).

Since Bengali has a four-way laryngeal contrast, VOT does not encode a binary voiced---voiceless distinction, and moreover is not the only cue for the corresponding phonological categories \citep{dmitrieva2020acoustic}. Thus, the effects of Bengali on English VOT are likely to be affected by additional phonological factors. Thus, avoiding any potential confounds was another reason we chose to focus on vowels as a target for transfer.
